Argennon: A Scalable Smart Contract Platform

### 2021-06-21 tex/sections/blockchain.tex
Add the forgotten parts
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

@@

@@

@@

\section{Governance}\label{sec:governance}

The Argennon Decentralized Autonomous Governance system (ADAGs)
\note{not yet written...}

@@

>>>>

\note{Explicit key registration enables Argennon to decouple cryptography from blockchain design. In this way,
    if the used cryptographic algorithms turn out to be insecure for some reason, for example because
    of the introduction of quantum computers, the cryptographic algorithms could be easily upgraded.}

@@

\subsection{Authorization}\label{subsec:txn-auth}

@@

While every block of the Argennon blockchain stores the commitment of the transaction list, Argennon does not enforce
storage of the transaction history. To be able to detect replay attacks, we require
every signature that a user creates to have a nonce. This nonce consists of the issuance round of the signature
and a sequence number: \texttt{(issuance,\ sequence)}. When a user creates more than one signature in a round, he
must sequence his signatures starting from 0 (i.e.~the sequence number restarts from 0 in every round). We define
a maximum lifetime for signatures, so a signature is invalid if \texttt{currentRound - issuance > maxLifeTime} or
if a signature of the same user with a bigger or equal nonce is already used
(i.e.~is recorded in the blockchain). A nonce is bigger than another nonce if it has an older issuance. If two
nonces have an equal issuance, the nonce with the bigger sequence number will be considered bigger.

To be able to detect invalid signatures, we keep the maximum nonce of used digital signatures per user. When the
difference between \texttt{issuance} component of this nonce and the current round becomes bigger than the
maximum allowed lifetime of a signature, this information can be safely deleted.\footnote{in some conventional
blockchains, the nonce data can never be deleted, even if the account has zero balance and is not used anymore.}

\subsection{Resource Declaration}\label{subsec:resource-declaration}

@@

@@

\section{Governance}\label{sec:governance}
The Argennon Decentralized Autonomous Governance system (ADAGs)
\note{not yet written...}

### 2021-06-21 tex/sections/consensus.tex
Add the forgotten parts
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

More precisely, to decide about signing the block certificate, every honest member of the validators
committee iterates over blocks of the validation set, and selects a block with
probability $p_u$. In this way, a member of the validators committee will select $p_{u}m$ blocks in expectation.
Then, the honest member conditionally validates the selected blocks. If the member has selected more than one block,
he may validate the selected blocks in parallel.
If all checked blocks are valid, the validator issues an "accept"
signature, otherwise he issues a "reject" signature.

@@

@@

Argennon users can lock their ARG tokens in their account for any period of time. During this time a user
will not be able to transfer his tokens and there is no way for cancelling a lock.
The trust value of a user is calculated based on the amount of his locked tokens and the
Exponential Moving Average (EMA) of his ARG balance:
\[
    Trust_{u,k} = \max (L_{u,k}, M_{u,t_k}),
\]
where
\begin{itemize}
    \item $L_{u,k}$ is the amount of locked tokens of user $u$, whose release time is \textbf{after the end} of
    the staking period $k+1$.
    \item $M_{u,t_k}$ is the Exponential Moving Average (EMA) of the ARG balance of user \(u\) at time step \(t_k\).
    $t_k$ is the start time of the staking period $k$.
\end{itemize}

@@

\subsection{The Recovery Protocol}\label{subsec:recovery}

\note{not yet written...}

>>>>

More precisely, to decide about signing the block certificate, a honest member of the validators
committee iterates over every block of the validation set, and selects a block for validation with
probability $p_u$. In this way, a member of the validators committee will select $p_{u}m$ blocks in expectation.
Then, the honest member conditionally validates the selected blocks. If the member has selected more than one block,
he may validate the selected blocks in parallel.
If all checked blocks are valid, the validator issues an "accept"
signature, otherwise he issues a "reject" signature.

@@

The value of $m$ is determined by the ADAGs. but it can never be set higher than $100$. This way, it is guaranteed
that on average, any block of the Argennon blockchain is validated by at least $0.005$ of the total ARG supply.

@@

Argennon users can lock their ARG tokens in their account for any period of time. During this time a user
will not be able to transfer his tokens and there is no way for cancelling a lock.
The trust value of a user is calculated based on the amount of his locked tokens and the
Exponential Moving Average (EMA) of his ARG balance:
\[
    Trust_{u,k} = L_{u,k} + M_{u,t_k}\ ,
\]
where
\begin{itemize}
    \item $L_{u,k}$ is the amount of locked tokens of user $u$, whose release time is \textbf{after the end} of
    the staking period $k+1$.
    \item $M_{u,t_k}$ is the Exponential Moving Average (EMA) of the ARG balance of user \(u\) at time step \(t_k\).
    $t_k$ is the start time of the staking period $k$.
\end{itemize}

@@

\subsection{The Recovery Protocol}\label{subsec:recovery}
\note{not yet written...}

\subsection{Analysis}\label{subsec:consensus-math}
\note{not yet written...}
